Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration

### 2025-01-08 doc/protocol.qmd
docs: :pencil2: small edit to title of protocol

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "2022-11-04"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---

@@

>>>>

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---

@@

<!-- TODO: Convert these to use the bib file -->
